Synthesising Termination and Non-Termination Proofs for Bit-Vector Programs

### 2014-07-08 papers/termination/paper.tex
units

Of the 47 benchmarks, 2 use nonlinear operations in the program (loop6 and loop11),
and 5 have nested loops (svcomp6, svcomp12, svcomp18, svcomp40, svcomp41).
{\sc Juggernaut} handles the nonlinear cases correctly and rapidly.
It solves 4 of the 5 nested loops in less than 30s\footnote{Although
2 of these cases timed out with our default parameters, changing one command
line flag allowed them to go through.  The benchmarks using non-default
command line flags are marked with a *.}, but times out on the 5th.

Overall, we notice that the GP component was always the fastest to find
candidate solutions, {\sc ExplicitSearch} was always fastest
to find counterexample inputs, and {\sc CBMC} was always fastest at
proving correctness.  Each of these search methods has its strengths,
and removing any one would have had a significant negative impact on
overall performance.  Approximately 90\% of the total
runtime was spent in synthesising new candidate solutions, which matches
our expectations -- the (non-)termination proofs are difficult to
find, but easy to check.

>>>>

Of the 47 benchmarks, 2 use nonlinear operations in the program (loop6 and loop11),
and 5 have nested loops (svcomp6, svcomp12, svcomp18, svcomp40, svcomp41).
{\sc Juggernaut} handles the nonlinear cases correctly and rapidly.
It solves 4 of the 5 nested loops in less than 30\,s\footnote{Although
2 of these cases timed out with our default parameters, changing one command
line flag allowed them to go through.  The benchmarks using non-default
command line flags are marked with a *.}, but times out on the 5th.

Overall, we notice that the GP component was always the fastest to find
candidate solutions, {\sc ExplicitSearch} was always fastest
to find counterexample inputs, and {\sc CBMC} was always fastest at
proving correctness.  Each of these search methods has its strengths,
and removing any one would have had a significant negative impact on
overall performance.  Approximately 90\,\% of the total
runtime was spent in synthesising new candidate solutions, which matches
our expectations -- the (non-)termination proofs are difficult to
find, but easy to check.
